The Galactic Delay-Time Distribution of Type Ia Supernovae:\\ A Chemical Evolution Perspective

### 2023-07-20 src/tex/ms.tex
[showyourwork] overleaf sync

% Main body with filler text
\section{Introduction}

@@

\begin{deluxetable*}{lll}
\tablecaption{Summary of SN Ia DTD models explored in this paper.\label{tab:dtds}}
\tablehead{
\colhead{Model} & \colhead{Parameters} & \colhead{Similar to}
}
\startdata
Power-law   & $\alpha=-1.1$                 & \citet[][field]{Maoz2017-CosmicDTD}; 
                                              \citet{Wiseman2021-DESRates}              \\
Power-law   & $\alpha=-1.4$                 & \citet[][cluster]{Maoz2017-CosmicDTD}; 
                                              \citet{Heringer2019-FieldGalaxyDTD}       \\
Plateau     & $W=0.3$ Gyr, $\alpha=-1.1$    & \citet[][CLOSE DD]{Greggio2005-AnalyticalRates} \\
Plateau     & $W=1.0$ Gyr, $\alpha=-1.1$    & \citet[][WIDE DD]{Greggio2005-AnalyticalRates} \\
Triple-system   & $f_{\rm init}=0.05f_{\rm peak}$, $t_{\rm rise}=0.5$ Gyr, & \citet{Rajamuthukumar2022-TripleEvolution} \\
            & $W=0.5$ Gyr, $\alpha=-1.1$ & \\
Exponential & $\tau=1.5$ Gyr    & \citet[][SD]{Greggio2005-AnalyticalRates};
                                  \citet{Schonrich2009-RadialMixing};       \\
            &                   & \citet{Weinberg2017-ChemicalEquilibrium}  \\
Exponential & $\tau=3.0$ Gyr    & \\
Prompt      & $t_{\rm max}=0.05$ Gyr, $\sigma=0.015$ Gyr, & \citet{Mannucci2006-TwoPopulations} \\
            & $\tau=3.0$ Gyr & \\
\enddata
\end{deluxetable*}

@@

Figure \ref{fig:sfhs} presents an overview of our model star formation histories.

@@

\paragraph{Inside-out}
\begin{equation}
    f_{\rm IO}(t|R_{\rm gal}) = (1 - e^{-t/\tau_{\rm rise}}) e^{-t/\tau_{\rm SFH}}
    \label{eq:insideout-sfh}
\end{equation}

\paragraph{Late-burst}
\begin{equation}
    f_{\rm LB}(t|R_{\rm gal}) = f_{\rm IO}(t|R_{\rm gal}) \Big(1 + A_b e^{-(t-t_b)^2/2\sigma_b^2} \Big)
    \label{eq:lateburst-sfh}
\end{equation}

\paragraph{Early-burst} The infall rate at a given radius declines exponentially with time:
\begin{equation}
    f_{\rm EB}(t|R_{\rm gal}) = e^{-t/\tau_{\rm IFR}}
    \label{eq:earlyburst-ifr}
\end{equation}
We take $\tau_{\rm IFR} = \tau_{\rm SFH}$ at all radii.
The time-dependence of the SFE timescale $\tau_*$ comes from \citet{Conroy2022-ThickDisk}:
\begin{equation}
    \frac{\tau_*(t|\Sigma_g)}{1\,\rm{Gyr}} =
    \begin{cases}
        50, & t < 2.5\,\rm{Gyr} \\
        \frac{50}{[1+3(t-2.5)]^2}, & 2.5\leq t \leq 3.7\,\rm{Gyr} \\
        2.36, & t > 3.7\,\rm{Gyr}
    \end{cases}
    \label{eq:earlyburst-conroy22}
\end{equation}
We combine this with the Kennicutt-Schmidt relation used by \citet{Johnson2021-Migration}, minus the dependence on the molecular timescale $\tau_{\rm mol}$:
\begin{equation}
    \dot \Sigma_* = 
    \begin{cases}
        \Sigma_g, & \Sigma_g \geq \Sigma_{g,2} \\
        \Sigma_g \Big(\frac{\Sigma_g}{\Sigma_{g,2}}\Big)^{2.6}, & \Sigma_{g,1} \leq \Sigma_g \leq \Sigma_{g,2} \\
        \Sigma_g \Big(\frac{\Sigma_{g,1}}{\Sigma_{g,2}}\Big)^{2.6} \Big(\frac{\Sigma_g}{\Sigma_{g,1}}\Big)^{0.7}, & \Sigma_g \leq \Sigma_{g,1}
    \end{cases}
    \label{eq:kennicutt-schmidt}
\end{equation}
Which leads to an overall SFE timescale of
\begin{equation}
    \tau_*(t,\Sigma_g) = \tau_*(t|\Sigma_g) \frac{\Sigma_g}{\dot \Sigma_*}
    \label{eq:earlyburst-taustar}
\end{equation}

@@

We use the same yields as in \citet{Johnson2021-Migration}.

@@

\begin{deluxetable*}{lll}
    \tablecaption{Sample Selection\label{tab:sample-selection}}
    \tablehead{
        \colhead{Parameter} & \colhead{Range} & \colhead{Notes}
    }
    \startdata
        $\log g$            & $1.0 < \log g < 3.8$          & Select giants only \\
        $T_{\rm eff}$       & $3500 < T_{\rm eff} < 5500$ K & Reliable temperature range \\
        $S/N$               & $S/N > 80$                    & Required for accurate stellar parameters \\
        ASPCAPFLAG Bits     & $\notin$ 23                   & Remove stars flagged as bad \\
        EXTRATARG Bits      & $\notin$ 0, 1, 2, 3, or 4     & Select main red star sample only \\
    \enddata
\end{deluxetable*}

@@

\section{Results from Single-Zone Models}
\label{sec:onezone-results}

All models are run for a duration of 13.2 Gyr with a simulation timestep of 0.01 Gyr.

@@

Figure \ref{fig:onezone-dtd} compares the one-zone model outputs from the full range of DTDs we investigate in this paper. In general, the choice of DTD has the greatest effect on the location of the knee in [Fe/H]-[O/Fe] space (center panel) and the high-$\alpha$ end of the distribution of [O/Fe] (right panel). The DTD also has a smaller effect on the MDF in the range $-15.5\lesssim$ [Fe/H] $\lesssim-0.5$ (top panel).

@@

Figure \ref{fig:onezone-dtd-delay} shows that the minimum SN Ia delay time has a much stronger effect on the abundance track and MDFs of models which assume a power-law DTD than models which assume an exponential, due to the much higher SN Ia rate in the power-law models at early times (see Figure \ref{fig:dtds}). Moreover, a power-law DTD with a long minimum delay may be observationally hard to distinguish from an exponential.

\begin{figure}
    \centering
    \includegraphics{figures/onezone_dtd_delay.pdf}
    \caption{Similar to Figure \ref{fig:onezone-slope-timescale} but with varying minimum SN Ia delay time ($t_D$). Dashed curves represent models with a minimum delay time of 40 Myr, while solid curves represent models with a minimum delay time of 150 Myr. The black curves represent a power-law DTD with a slope of $-1.1$, while the blue curves represent an exponential DTD with a timescale of 1.5 Gyr.}
    \label{fig:onezone-dtd-delay}
    \script{onezone_dtd_delay.py}
\end{figure}

A 150 Myr minimum delay time is incompatible with the prompt DTD model, which has $\sim 50$\% of SNe Ia explode in the first 100 Myr.

@@

\begin{figure}
    \centering
    \includegraphics{figures/onezone_delay_taustar.pdf}
    \caption{Similar to Figure \ref{fig:onezone-powerlaw-slope} but with varying minimum SN Ia delay time ($t_D$) and star formation efficiency timescale ($\tau_*$). Tracks with $\tau_*=2$ Gyr are represented in black, while a track with a shorter $\tau_*=1$ Gyr is shown in red and a track with a longer $\tau_*=4$ Gyr is in yellow. The dotted, solid, and dashed black curves represent a minimum delay time of 40 Myr, 80 Myr, and 160 Myr, respectively. A power-law DTD is assumed in all models.}
    \label{fig:onezone-delay-taustar}
    \script{onezone_delay_taustar.py}
\end{figure}

@@

\begin{deluxetable}{lll}
    \tablecaption{Median Parameter Uncertainties\label{tab:uncertainties}}
    \tablehead{
        \colhead{Parameter} & \colhead{Median Uncertainty} & \colhead{Source}
    }
    \startdata
        [Fe/H] & $9.2\times10^{-3}$ & APOGEE \\
        $\rm [O/Fe]$ & $1.8\times10^{-2}$ & APOGEE \\
        log(Age/Gyr) & $0.12$ & \citet{Leung2023-Ages}
        % Age/Gyr & 29\% & astroNN
    \enddata
\end{deluxetable}

\subsection{Comparison to APOGEE MDFs}

@@

\begin{figure*}
    \centering
    \includegraphics{figures/feh_df_sfh.pdf}
    \caption{Distributions of [Fe/H] for multi-zone simulations with different SFHs. Each row presents distributions of stars within a range of absolute midplane distance: $1\leq|z|<2$ kpc (\textit{top}), $0.5\leq|z|<1$ kpc (\textit{middle}), and $0\leq|z|<0.5$ kpc (\textit{bottom}). Within each panel, curves of different color represent the distributions of stars binned by Galactocentric radius $R_{\rm gal}$, from $3\leq R_{\rm gal}<5$ kpc (yellow) to $13\leq R_{\rm gal}<15$ kpc (blue). }
    \label{fig:feh-df-sfh}
    \script{feh_df_sfh.py}
\end{figure*}

\subsection{Comparison to APOGEE ODFs}

\begin{figure*}
    \centering
    \includegraphics{figures/ofe_df_dtd.pdf}
    \caption{Caption.}
    \label{fig:ofe-df-dtd}
    \script{ofe_df_dtd.py}
\end{figure*}

\begin{figure*}
    \centering
    \includegraphics{figures/ofe_df_sfh.pdf}
    \caption{Caption.}
    \label{fig:ofe-df-sfh}
    \script{ofe_df_sfh.py}
\end{figure*}

>>>>

\section{Introduction}

@@

\begin{deluxetable*}{lll}
\tablecaption{Summary of SN Ia DTD models explored in this paper.\label{tab:dtds}}
\tablehead{
\colhead{Model} & \colhead{Parameters} & \colhead{Similar to}
}
\startdata
Power-law   & $\alpha=-1.1$                 & \citet[][field]{Maoz2017-CosmicDTD}; 
                                              \citet{Wiseman2021-DESRates}              \\
Power-law   & $\alpha=-1.4$                 & \citet[][cluster]{Maoz2017-CosmicDTD}; 
                                              \citet{Heringer2019-FieldGalaxyDTD}       \\
Plateau     & $W=0.3$ Gyr, $\alpha=-1.1$    & \citet[][CLOSE DD]{Greggio2005-AnalyticalRates} \\
Plateau     & $W=1.0$ Gyr, $\alpha=-1.1$    & \citet[][WIDE DD]{Greggio2005-AnalyticalRates} \\
Triple-system   & $f_{\rm init}=0.05f_{\rm peak}$, $t_{\rm rise}=0.5$ Gyr, & \citet{Rajamuthukumar2022-TripleEvolution} \\
            & $W=0.5$ Gyr, $\alpha=-1.1$ & \\
Exponential & $\tau=1.5$ Gyr    & \citet[][SD]{Greggio2005-AnalyticalRates};
                                  \citet{Schonrich2009-RadialMixing};       \\
            &                   & \citet{Weinberg2017-ChemicalEquilibrium}  \\
Exponential & $\tau=3.0$ Gyr    & --- \\
Prompt      & $t_{\rm max}=0.05$ Gyr, $\sigma=0.015$ Gyr, & \citet{Mannucci2006-TwoPopulations} \\
            & $\tau=3.0$ Gyr & \\
\enddata
\end{deluxetable*}

@@

In this paper, we consider four models for the SFH: inside-out, late-burst, early-burst, and two-infall. The first two models are run in VICE's ``star formation mode,'' where the surface density of star formation rate $\dot\Sigma_*$ is prescribed along with the star formation efficiency timescale $\tau_*$, and the infall rate surface density $\dot\Sigma_{\rm in}$ and gas surface density $\Sigma_{\rm gas}$ are calculated from the specified quantities. The latter two models are run in ``infall mode,'' where we specify $\dot\Sigma_{\rm in}$  and $\tau_*$ and the other two quantities follow.

The functions presented below are dimensionless. For a detailed look at the normalization of the star formation rate with $R_{\rm gal}$, we refer the reader to Appendix B of \citet{Johnson2021-Migration}.

\paragraph{Inside-out} Following \citet{Johnson2021-Migration}, this is our fiducial SFH:
\begin{equation}
    f_{\rm IO}(t|R_{\rm gal}) = (1 - e^{-t/\tau_{\rm rise}}) e^{-t/\tau_{\rm sfh}}
    \label{eq:insideout-sfh}
\end{equation}
where we assume $\tau_{\rm rise}=2$ Gyr for all radii. The SFH timescale $\tau_{\rm sfh}$ varies with $R_{\rm gal}$, with $\tau_{\rm sfh}(R_{\rm gal}=8\,\rm{kpc})\approx15$ Gyr at the Solar annulus and longer timescales in the outer galaxy. The $\tau_{\rm sfh} - R_{\rm gal}$ relation is determined from the data of \citet{Sanchez2020-StarFormationTimescales}; see Section 2.5 of \citet{Johnson2021-Migration} for the details.

\paragraph{Late-burst} A variation on the inside-out SFH with a Gaussian burst in the star formation rate:
\begin{equation}
    f_{\rm LB}(t|R_{\rm gal}) = f_{\rm IO}(t|R_{\rm gal}) \Big(1 + A_b e^{-(t-t_b)^2/2\sigma_b^2} \Big)
    \label{eq:lateburst-sfh}
\end{equation}
where $A_b$ is the dimensionless amplitude of the starburst, $t_b$ is the time of the peak of the burst, and $\sigma_b$ is the width of the Gaussian. Following \citet{Johnson2021-Migration}, we adopt $A_b=1.5$, $t_b=11.2$ Gyr, and $\sigma_b=1$ Gyr. The determination of $\tau_{\rm sfh}$ and the normalization of the SFR as a function of $R_{\rm gal}$ are the same as in the inside-out case.

\paragraph{Early-burst} The infall rate at a given radius declines exponentially with time:
\begin{equation}
    f_{\rm EB}(t|R_{\rm gal}) = e^{-t/\tau_{\rm sfh}}
    \label{eq:earlyburst-ifr}
\end{equation}
The time-dependence of the SFE timescale $\tau_*$ comes from \citet{Conroy2022-ThickDisk}:
\begin{equation}
    \frac{\tau_*(t|\Sigma_g)}{1\,\rm{Gyr}} =
    \begin{cases}
        50, & t < 2.5\,\rm{Gyr} \\
        \frac{50}{[1+3(t-2.5)]^2}, & 2.5\leq t \leq 3.7\,\rm{Gyr} \\
        2.36, & t > 3.7\,\rm{Gyr}
    \end{cases}
    \label{eq:earlyburst-conroy22}
\end{equation}
We combine this with the Kennicutt-Schmidt relation used by \citet{Johnson2021-Migration}, minus the dependence on the molecular timescale $\tau_{\rm mol}$:
\begin{equation}
    \dot \Sigma_* = 
    \begin{cases}
        \Sigma_g, & \Sigma_g \geq \Sigma_{g,2} \\
        \Sigma_g \Big(\frac{\Sigma_g}{\Sigma_{g,2}}\Big)^{2.6}, & \Sigma_{g,1} \leq \Sigma_g \leq \Sigma_{g,2} \\
        \Sigma_g \Big(\frac{\Sigma_{g,1}}{\Sigma_{g,2}}\Big)^{2.6} \Big(\frac{\Sigma_g}{\Sigma_{g,1}}\Big)^{0.7}, & \Sigma_g \leq \Sigma_{g,1}
    \end{cases}
    \label{eq:kennicutt-schmidt}
\end{equation}
Which leads to an overall SFE timescale of
\begin{equation}
    \tau_*(t,\Sigma_g) = \tau_*(t|\Sigma_g) \frac{\Sigma_g}{\dot \Sigma_*}
    \label{eq:earlyburst-taustar}
\end{equation}

Figure \ref{fig:sfhs} presents an overview of these model star formation histories.

@@

@@

Table \ref{tab:yields} summarizes the nucleosynthetic yields assumed in this paper, which we adopt from \citet{Johnson2021-Migration}.

@@

\begin{deluxetable*}{lll}
    \tablecaption{Sample selection parameters from APOGEE DR17\label{tab:sample-selection}}
    \tablehead{
        \colhead{Parameter} & \colhead{Range} & \colhead{Notes}
    }
    \startdata
        $\log g$            & $1.0 < \log g < 3.8$          & Select giants only \\
        $T_{\rm eff}$       & $3500 < T_{\rm eff} < 5500$ K & Reliable temperature range \\
        $S/N$               & $S/N > 80$                    & Required for accurate stellar parameters \\
        ASPCAPFLAG Bits     & $\notin$ 23                   & Remove stars flagged as bad \\
        EXTRATARG Bits      & $\notin$ 0, 1, 2, 3, or 4     & Select main red star sample only \\
    \enddata
\end{deluxetable*}

@@

\section{Results from One-Zone Models}
\label{sec:onezone-results}

All models are run for a duration of $t_{\rm max}=13.2$ Gyr with a time-step of $\Delta t=0.01$ Gyr. We adopt an outflow mass-loading factor $\eta\equiv \dot M_{\rm out}/\dot M_*=2.15$ \citep[see Equation 8 from][]{Johnson2021-Migration} and a star formation efficiency timescale $\tau_*\equiv M_{\rm gas}/\dot M_*=2$ Gyr. We adopt a continuous recycling prescription \citep[see Equation 2 from][]{JohnsonWeinberg2020-Starbursts}. Unless otherwise specified, we adopt the inside-out star formation rate (Equation \ref{eq:insideout-sfh}) evaluated at $R_{\rm gal}=8$ kpc, with timescales $\tau_{\rm rise}=2$ Gyr and $\tau_{\rm sfh}=15.1$ Gyr, and our models have an initial gas mass $M_{\rm gas,0}=0$. Unless otherwise specified, we assume a minimum SN Ia delay time of 40 Myr. A summary of these one-zone fiducial parameters is presented in Table \ref{tab:onezone-parameters}.

\begin{deluxetable}{Ccl}
    \tablecaption{A summary of parameters and their fiducial values for our one-zone chemical evolution models.\label{tab:onezone-parameters}}
    \tablehead{
        \colhead{Parameter} & \colhead{Value} & \colhead{Description}
    }
    \startdata
    \Delta t        & 10 Myr    & Time-step size \\
    t_{\rm max}     & 13.2 Gyr  & Maximum simulation time \\
    \eta            & 2.15      & Outflow mass-loading factor \\
    \tau_*          & 2.0 Gyr   & Star formation efficiency timescale \\
    \dot M_r        & continuous    & Recycling rate \\
    t_D             & 40 Myr    & Minimum SN Ia delay time \\
    M_{\rm gas,0}   & 0         & Initial gas mass \\
    \dot M_*(t)     & Equation \ref{eq:insideout-sfh}  & Star formation rate \\
    \tau_{\rm rise} & 2 Gyr     & SFR rise timescale \\
    \tau_{\rm sfh}  & 15.1 Gyr  & SFR exponential timescale
    \enddata
\end{deluxetable}

@@

Figure \ref{fig:onezone-dtd} compares the one-zone model outputs from the full range of DTDs we investigate in this paper. In general, the choice of DTD has the greatest effect on the location of the knee in [Fe/H]-[O/Fe] space (center panel) and the high-$\alpha$ end of the distribution of [O/Fe] (right panel). The DTD also has a smaller effect on the MDF in the range $-1.5\lesssim$ [Fe/H] $\lesssim-0.5$ (top panel).

@@

Figure \ref{fig:onezone-minimum-delay} shows that the minimum SN Ia delay time has a much stronger effect on the abundance track and MDFs of models which assume a power-law DTD than models which assume a plateau or exponential DTD, due to the much higher SN Ia rate in the power-law models at early times (see Figure \ref{fig:dtds}). Moreover, a power-law DTD with a long minimum delay may be observationally hard to distinguish from a plateau model. In Figure \ref{fig:onezone-minimum-delay}, the abundance track for the model with a power-law DTD and $t_D=150$ Myr (red dashed line) is similar to that of the plateau DTD with $W=0.3$ Gyr and $t_D=40$ Myr (blue solid line), and the [O/Fe] distributions are virtually identical.

\begin{figure}
    \centering
    \includegraphics{figures/onezone_minimum_delay.pdf}
    \caption{Similar to Figure \ref{fig:onezone-powerlaw-slope} but with varying DTD models and minimum SN Ia delay time ($t_D$). Solid curves represent models with a minimum delay time of 40 Myr, while dashed curves represent models with a minimum delay time of 150 Myr. The red curves represent a power-law DTD with slope $\alpha=-1.1$; blue curves represent an plateau DTD with width $W=0.3$ Gyr and slope $\alpha=-1.1$; and orange curves represent an exponential DTD with timescale $\tau=3$ Gyr. In all cases an exponential rise-fall SFR is assumed.}
    \label{fig:onezone-minimum-delay}
    \script{onezone_minimum_delay.py}
\end{figure}

A 150 Myr minimum delay time is incompatible with the prompt DTD model, which has $\sim 50$\% of SNe Ia explode in the first 100 Myr, and would have a negligible effect on the triple-system DTD as its relative SN Ia rate is so low at early times.

@@

\begin{figure}
    \centering
    \includegraphics{figures/onezone_delay_taustar.pdf}
    \caption{Similar to Figure \ref{fig:onezone-powerlaw-slope} but with varying minimum SN Ia delay time ($t_D$) and star formation efficiency timescale ($\tau_*$). Tracks with $\tau_*=2$ Gyr are represented in black, while a track with a shorter $\tau_*=1$ Gyr is shown in red and a track with a longer $\tau_*=4$ Gyr is in yellow. The dotted, solid, and dashed black curves represent a minimum delay time of 40 Myr, 80 Myr, and 160 Myr, respectively. A power-law DTD with $\alpha=-1.1$ is assumed in all models.}
    \label{fig:onezone-delay-taustar}
    \script{onezone_delay_taustar.py}
\end{figure}

@@

\begin{deluxetable}{lll}
    \tablecaption{Median Parameter Uncertainties\label{tab:uncertainties}}
    \tablehead{
        \colhead{Parameter} & \colhead{Median Uncertainty} & \colhead{Source}
    }
    \startdata
        [Fe/H] & $9.2\times10^{-3}$ & APOGEE DR17 \\
        $\rm [O/Fe]$ & $1.8\times10^{-2}$ & APOGEE DR17 \\
        log(Age/Gyr) & $0.12$ & \citet{Leung2023-Ages}
        % Age/Gyr & 29\% & astroNN
    \enddata
\end{deluxetable}

\subsection{The distribution of [Fe/H]}

@@

Figure \ref{fig:feh-df-sfh} plots the distribution of [Fe/H] in multiple regions across the disk for the four SFHs in this paper.

\begin{figure*}
    \centering
    \includegraphics{figures/feh_df_sfh.pdf}
    \caption{Distributions of [Fe/H] for multi-zone simulations with different SFHs. Each row presents distributions of stars within a range of absolute midplane distance: $1\leq|z|<2$ kpc (\textit{top}), $0.5\leq|z|<1$ kpc (\textit{middle}), and $0\leq|z|<0.5$ kpc (\textit{bottom}). Within each panel, curves of different color represent the distributions of stars binned by Galactocentric radius $R_{\rm gal}$, from $3\leq R_{\rm gal}<5$ kpc (yellow) to $13\leq R_{\rm gal}<15$ kpc (blue). Each distribution is normalized so the area under the curve is 1, and the vertical scale is consistent across each row. All distributions are convolved with observational uncertainties in APOGEE DR17 (see Table \ref{tab:uncertainties}) and smoothed with a box-car width of 0.2 dex. In all cases an exponential DTD with timescale $\tau=1.5$ Gyr is assumed. Distributions from APOGEE DR17, binned similarly, are presented in the right-most column for reference.}
    \label{fig:feh-df-sfh}
    \script{feh_df_sfh.py}
\end{figure*}

Holding the SFH fixed, varying the DTD has only a minor effect on the MDF. Figure \ref{fig:feh-df-dtd} plots the [Fe/H] distributions for two multi-zone simulations which both assume an inside-out SFH but different DTDs: a power-law with slope $\alpha=-1.4$, and an exponential with timescale $\tau=3$ Gyr. The balance between prompt and delayed SNe Ia is starkly different between the two models, with $\sim 80\%$ of SNe Ia exploding within 1 Gyr in the former model but only $\sim 30\%$ in the latter. Nevertheless, the effect of the DTD on the MDF is second-order compared to the effect of the SFH as seen in Figure \ref{fig:feh-df-sfh}.

\begin{figure}
    \centering
    \includegraphics{figures/feh_df_dtd.pdf}
    \caption{Distributions of [Fe/H] for multi-zone simulations with different DTDs: a power-law with slope $\alpha=-1.4$ (\textit{left}), and an exponential with timescale $\tau=3$ Gyr (\textit{right}). In both cases an inside-out SFH is assumed. The plot format is similar to Figure \ref{fig:feh-df-sfh}.}
    \label{fig:feh-df-dtd}
    \script{feh_df_dtd.py}
\end{figure}

\subsection{The distribution of [O/Fe]}

\begin{figure*}
    \centering
    \includegraphics{figures/ofe_df_dtd.pdf}
    \caption{Distributions of [O/Fe] for multi-zone simulations with different DTDs. In all cases an inside-out SFH is assumed. The plot format is similar to Figure \ref{fig:feh-df-sfh}. All distributions are smoothed with a box-car width of 0.05 dex.}
    \label{fig:ofe-df-dtd}
    \script{ofe_df_dtd.py}
\end{figure*}

\begin{figure*}
    \centering
    \includegraphics{figures/ofe_df_sfh.pdf}
    \caption{Distributions of [O/Fe] for multi-zone simulations with different SFHs. The plot format is similar to Figure \ref{fig:feh-df-sfh}. In all cases an exponential DTD with timescale $\tau=1.5$ Gyr is assumed.}
    \label{fig:ofe-df-sfh}
    \script{ofe_df_sfh.py}
\end{figure*}

\subsection{The [O/Fe]--[Fe/H] Plane}
\label{sec:ofe-feh}

\begin{figure}
    \centering
    \includegraphics{figures/ofe_feh_sfh.pdf}
    \caption{Caption}
    \label{fig:ofe-feh-sfh}
    \script{ofe-feh-sfh.py}
\end{figure}

\begin{figure*}
    \centering
    \includegraphics{figures/ofe_feh_dtd.pdf}
    \caption{Caption}
    \label{fig:ofe-feh-dtd}
    \script{ofe-feh-dtd.py}
\end{figure*}
